### 2022-01-28 paper/paper.tex
methodology: add metrics and backend

% Links
\usepackage{hyperref}
\hypersetup{
	pdftitle={Development of a touch typing trainer with an emphasis on finger and wrist placement},
	pdfstartview={FitH},
	colorlinks=true,
	linkcolor=black,
	citecolor=black,
	filecolor=black,
	urlcolor=MidnightBlue
}

@@

	\textsc{Development of a touch typing trainer\\with an emphasis on finger and wrist positions}
	\par\vspace{0.5cm}

@@

	October 2021
	\vfill
	\hspace{0pt}
\end{titlepage}
\newpage

@@

The experimental setup and configuration will be composed of three elements: the
camera, the keyboard, and the environment. Figure~\ref{fig:metho-setup-cam}
shows the sketch of the complete experimental setup.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\textwidth]{webcam.png}
	\caption{Sketch of the experimental setup}
	\label{fig:metho-setup-cam}
	\centering
\end{figure}

@@

There will be 15 videos of the researcher performing the typing test sequences.
The researcher will then manually perform finger-key identification for all key
presses present in the video. The finger-key identification submodule will then
perform the same process for the same videos. The accuracy of the submodule will
then be obtained by identifying which of its identification is incorrect, based
on the manual identification.

@@

>>>>

% Links
\usepackage{hyperref}
\hypersetup{
	pdftitle={Development of a touch typing trainer with an emphasis on finger-key identification},
	pdfstartview={FitH},
	colorlinks=true,
	linkcolor=black,
	citecolor=black,
	filecolor=black,
	urlcolor=MidnightBlue
}

@@

	\textsc{Development of a touch typing trainer\\with an emphasis on finger-key identification }
	\par\vspace{0.5cm}

@@

	February 2022
	\vfill
	\hspace{0pt}
\end{titlepage}
\newpage

@@

The experimental setup and configuration will be composed of three elements: the
camera, the keyboard, and the environment. Figure~\ref{fig:metho-setup}
shows the sketch of the complete experimental setup.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\textwidth]{setup.png}
	\caption{Sketch of the experimental setup}
	\label{fig:metho-setup}
	\centering
\end{figure}

@@

There will be 15 videos of the researcher performing the typing test sequences.
The researcher will then manually perform finger-key identification for all key
presses present in the video. The finger-key identification submodule will then
perform the same process for the same videos. The accuracy of the submodule will
then be obtained by identifying if its identification is as expected, based on
the manual identification.

@@

\subsection{Per Test Sequence}
The metric to be calculated per test sequence is Finger Placement Accuracy (FP
ACC). This metric will compute the percentage of accurate key presses pressed
with the correct finger over the length of the typing test sequence. Inputting
the wrong character, even if pressed with the correct finger will reduce FP ACC
since FP ACC measures \emph{accurate key presses}, and incorrect characters will
be considered as inaccurate key presses.

The equation for calculating FP ACC is as follows:

\begin{equation}
	FP ACC = \frac{|F|}{|T|} \cdot 100\%
\end{equation}

Where $|F|$ refers to the number of accurate key presses pressed with the
correct finger and $|T|$ refers to the length of the text.

\subsection{Per Key}
This metric will compute the Historical Finger Placement Accuracy (HFP ACC) for
a certain key. This will include the times the user pressed the wrong key when
asked for a certain character, the same as in FP ACC. This will allow the user
to easily verify which keys need attention and retraining if there is a high
frequency of error.

The equation for calculating a key's HFP ACC is as follows:

\begin{equation}
	HFP ACC = \frac{|F_{char}|}{|C_{char}|} \cdot 100\%
\end{equation}

Where $|F_{char}|$ refers to the number of accurate key presses pressed with the
correct finger for a certain character, identified as $char$. $|C_{char}|$
refers to the number of times the character has appeared in all test sequences
for the user.
